State-space analysis of continuous gravitational waves with a pulsar timing array: inclusion of the pulsar terms

### 2023-11-27 manuscript/manuscript_2/paper.tex
bayes for multiple strains

>>>>

\textcolor{red}{TK: there is an obvious additional feature that I haven't yet mentioned in the text, which is the systematic offset in iota and h w.r.t the injection. I think this is likely a sampler setting. I am currently running some checks, and will then add few sentences discussing this, or update the results/plots.}
